Higgs Assisted Razor Search for Higgsinos at 100 TeV

### 2019-07-20 main.tex

Searches for pair produced nearly mass-degenerate Higgsinos  have been
performed at ATLAS and CMS for various decay  topologies\cite{Aaboud:2018htj,Sirunyan:2018ubx,Aaboud:2018zeb}.  For neutralino-chargino pair production with $WZ$ and $WH$ topologies, the 95\% C.L. exclusion limits are about 650 GeV, 490 GeV, and 535 GeV for $WZ$, $WH$ and an equal mixture of $WZ+WH$ topology, with the most stringest limits from the multi-lepton searches.  For neutralino pair production with $ZZ$, $ZH$ and $HH$ topologies~\footnote{While such searches assume gravitino LSP with Higgsino NLSP, the limits are still relevant for our Higgsino NLSP with Bino LSP scenario.}, the limits are about 650 $-$ 750 GeV via multi-lepton or multi-$b$ jets searches, depending on the decay branching fractions of Higgsino NLSP.

>>>>

Searches for pair produced nearly mass-degenerate Higgsinos  have been
performed at ATLAS and CMS for various decay  topologies
\cite{Aaboud:2018htj,Sirunyan:2018ubx,Aaboud:2018zeb}.  
For neutralino-chargino pair production with $WZ$ and $WH$ topologies, the 95\% C.L. exclusion limits are about 650 GeV, 490 GeV, and 535 GeV for $WZ$, $WH$ and an equal mixture of $WZ+WH$ topology, with the most stringest limits from the multi-lepton searches.  For neutralino pair production with $ZZ$, $ZH$ and $HH$ topologies~\footnote{While such searches assume gravitino LSP with Higgsino NLSP, the limits are still relevant for our Higgsino NLSP with Bino LSP scenario.}, the limits are about 650 $-$ 750 GeV via multi-lepton or multi-$b$ jets searches, depending on the decay branching fractions of Higgsino NLSP.
